### 2021-02-19 ch01_introduction/introduction.tex
Finished section 6.1

\section{Key Science Questions}
\label{sec:01:research_questions}

This section will present the \textbf{AWESOME} key science questions!!!

@@

Parts of this thesis are already published in multiple peer-reviewed
publications (two first-author studies and six co-author studies). Wherever
material from these studies is presented in this thesis, the pronoun
\enquote{we} is used to increase readability by avoiding the passive voice and
to acknowledge all involved contributors. However, unless stated otherwise, all
contents from these publications (text, figures and tables) shown in this
thesis originate from the author of this thesis. A detailed list of
contributions to these studies (including their full reference) is given in the
corresponding chapters.

This thesis is structured as follows: \Cref{ch:02:scientific_background}
introduces the scientific background. This includes relevant literature that is
used as a baseline for this thesis. \Cref{ch:03:esmvaltool} gives an overview
over the contributions made to the \ac{ESMValTool}, an open-source software for
the analysis of \acp{ESM}. These contributions helped improving the routine
evaluation of \acp{ESM} which is useful for the entire scientific community and
lead to co-authorship in four peer-reviewed studies \autocite{Eyring2020,
  Lauer2020, Righi2020, Weigel2020}. \Cref{ch:04:papers_ecs_tcr_assessment}
covers the assessment of climate sensitivity metrics like the \ac{ECS} or
\ac{TCR} in the latest generation of \acp{ESM} (\acs{CMIP}6). This work is
already published in two scientific publications \autocite{Bock2020,
  Meehl2020}. Since the \ac{ECS} and \ac{TCR} are considerably higher in this
new climate model generation, \cref{ch:05:paper_ecs} describes the assessment
of emergent constraints (a technique to reduce uncertainties in multi-model
climate projections, see \cref{subsec:02:emergent_constraints}) on the \ac{ECS}
for these \acp{ESM}. The contents of this chapter are published in \emph{Earth
  System Dynamics} \autocite{Schlund2020a}. \Cref{ch:06:paper_gpp} focuses on a
new method to reduce uncertainties in gridded multi-model projections of the
future climate with observations based on \ac{ML}. As an example, the method is
applied to the photosynthesis rate at the end of the \nth{21} century, which is
already published in the \emph{Journal of Geophysical Research: Biogeosciences}
\autocite{Schlund2020}. Finally, \cref{ch:07:summary_outlook} provides a
summary of the results of this thesis and gives an outlook of possible future
works.

>>>>

\section{Key Science Questions}
\label{sec:01:key_science_questions}

This \namecref{sec:01:key_science_questions} will present the \textbf{AWESOME}
key science questions!!!

@@

Parts of this thesis are already published in multiple peer-reviewed
publications (two first-author studies and six co-author studies). Wherever
material from these studies is presented in this thesis, the pronoun
\enquote{we} is used to increase readability by avoiding the passive voice and
to acknowledge all involved contributors. However, unless stated otherwise, all
contents from these publications (text, figures and tables) shown in this
thesis originate from the author of this thesis. A detailed list of
contributions to these studies (including their full reference) is given in the
corresponding \namecrefs{ch:03:esmvaltool}.

This thesis is structured as follows: \Cref{ch:02:scientific_background}
introduces the scientific background. This includes relevant literature that is
used as a baseline for this thesis. \Cref{ch:03:esmvaltool} gives an overview
over the contributions made to the \ac{ESMValTool}, an open-source software for
the analysis of \acp{ESM}. These contributions helped improving the routine
evaluation of \acp{ESM} which is useful for the entire scientific community and
lead to co-authorship in four peer-reviewed studies \autocite{Eyring2020,
  Lauer2020, Righi2020, Weigel2020}. \Cref{ch:04:papers_ecs_tcr_assessment}
covers the assessment of climate sensitivity metrics like the \ac{ECS} or
\ac{TCR} in the latest generation of \acp{ESM} (\acs{CMIP}6). This work is
already published in two scientific publications \autocite{Bock2020,
  Meehl2020}. Since the \ac{ECS} and \ac{TCR} are considerably higher in this
new climate model generation, \cref{ch:05:paper_ecs} describes the assessment
of emergent constraints (a technique to reduce uncertainties in multi-model
climate projections, see \cref{subsec:02:emergent_constraints}) on the \ac{ECS}
for these \acp{ESM}. The contents of this \namecref{ch:05:paper_ecs} are
published in \emph{Earth System Dynamics} \autocite{Schlund2020a}.
\Cref{ch:06:paper_gpp} focuses on a new method to reduce uncertainties in
multi-dimensional (gridded) multi-model projections of the future climate with
observations based on \ac{ML}. As an example, the method is applied to the
photosynthesis rate at the end of the \nth{21} century, which is already
published in the \emph{Journal of Geophysical Research: Biogeosciences}
\autocite{Schlund2020}. Finally, \cref{ch:07:summary_outlook} provides a
summary of the results of this thesis and gives an outlook of possible future
works.

### 2021-02-19 ch02_scientific_background/scientific_background.tex
Finished section 6.1

This chapter introduces the scientific background of this thesis. First, basic
concepts of climate model simulations and associated uncertainties are
introduced (\cref{sec:02:esms}). Next, important metrics describing climate
sensitivity (\cref{sec:02:climate_sensitivity}) and fundamental biogeochemical
processes of the global carbon cycle (\cref{sec:02:esms}) are presented.
Finally, state-of-the art techniques that can be used to reduce uncertainties
in projections of the future climate with observations are shown
(\cref{sec:02:reducing_uncertainties}). These methods form the basis for new
techniques developed in this thesis.

@@

In this thesis, climate model data from the two most recent \ac{CMIP}
generations is used, \acs{CMIP}5 and \acs{CMIP}6. More detailed information
about the specific variables and experiments analyzed is given in the
corresponding chapters.

@@

\emph{Natural variability} is connected to the chaotic nature of the Earth
system that arises from complex interactions between the ocean, atmosphere,
land, biosphere and cryosphere \autocite{Cubasch2013}. It constitutes a
fundamental limit of how precisely we can project the future climate since it
is inherent in the Earth system and cannot be eliminated by more knowledge and
more advanced climate models. Natural variability is more relevant on regional
and local scales than on continental or global scales. Further contributions to
natural variability on longer time scales come from phenomena like the
\ac{ENSO} or the \ac{NAO} and from externally (and thus explainable) events
like volcanic eruptions and variations in the solar activity. Natural
variability can be seen as the \emph{noise} in the climate record as opposed to
the anthropogenic \emph{signal} \autocite{Cubasch2013}. As illustrated by
\cref{fig:02:sources_of_uncertainty}, the uncertainty associated with natural
variability is constant over time.

@@

As sciences evolves, representations of already included processes can be
improved in climate models. Moreover, new geophysical and biogeochemical
processes can be added to them. On the one hand, this can increase the climate
response uncertainty when a new process is discovered to be relevant
\commentcite{Cubasch2013}{see \cref{fig:02:sources_of_uncertainty}b}. However,
such an increase corresponds to a previously unmeasured uncertainty. An example
for this has recently happened in \acs{CMIP}6: most likely due to changes in
the cloud representation of the models the spread in the projected \ac{GSAT}
caused by a doubling of the atmospheric \ac{CO2} concentration has
substantially increased in \acs{CMIP}6 compared to older \ac{CMIP} generations
\autocite{Zelinka2020}. On the other hand, the climate response uncertainty can
decrease with additional model improvements and better understanding of the
Earth system (see \cref{fig:02:sources_of_uncertainty}c). Moreover, it can also
be reduced by observational constraints, which is the main topic of this
thesis.

@@

Since one study presented in this thesis aims to reduce uncertainties in carbon
cycle--related processes \commentcite{Schlund2020}{see \cref{ch:06:paper_gpp}},
this chapter introduces the scientific background of the global carbon cycle.

@@

Thus, more sophisticated techniques are necessary to evaluate multi-model
climate projections. This section introduces three state-of-the-art methods to
assess multi-model projections and reduce associated uncertainties with
observations. These techniques form the baseline of the work presented in the
following chapters.

@@

As indicated at the beginning of this section, one main issue of multi-model
ensembles is that not all participating climate models are equally plausible.
Usually, this is quantified with some kind of measure of the models'
\emph{performance}, \ie{} their agreement with observations of the real climate
system. However, this model performance can only be evaluated against
observations of the past and present-day climate, which does not necessarily
provide insights into the quality of model projections of the future climate.

@@

A further technique to reduce uncertainties in climate model projections with
observations are model weighting schemes. Their basic idea is to abandon model
democracy by replacing the arithmetic mean used to calculate the \acp{MMM} by a
weighted mean of the form
\begin{equation}
  y = \sum_{m=1}^{M} w_m y_m
  \label{eq:02:weighted_mean}
\end{equation}
with normalized weights $w_m$. Similar to the notation introduced in the
previous section, $y$ is a target variable (\eg{} a projection of the future
climate) and $m$ indexes the $M$ different climate models. To address two major
issues of model democracy (different climate models are not equally plausible
and not independent; see beginning of \cref{sec:02:reducing_uncertainties}),
\textcite{Knutti2017a} propose a weighting scheme based on climate model
performance and interdependence with the following weights:
\begin{equation}
  w_m \propto \frac{\exp \left( -\frac{D_m^2}{\sigma_D^2} \right)}{1 + \sum_{n
    \neq m}^{M} \exp \left( -\frac{S_{mn}^2}{\sigma_S^2} \right)}.
  \label{eq:02:knutti_weights}
\end{equation}
The metric $D_m$ describes the distance between climate model $m$ and
observations (= model performance) and the metric $S_{mn}$ describes the
distance between climate model $m$ and $n$ (= model interdependence).
$\sigma_D$ and $\sigma_S$ are constants that determine the individual strength
of the performance and interdependence weighting, respectively.

@@

The constants $\sigma_D$ and $\sigma_S$ determine how strongly the climate
models' performance and interdependence are weighted \autocite{Knutti2017a}.
Small values of the performance parameter $\sigma_D$ lead to an aggressive
weighting with only a few climate models receiving a majority of the weight,
while large values of $\sigma_D$ result in an equal weighting. For the
interdependence parameter $\sigma_S$, this is slightly different: Here, small
(all climate models are independent) and large (all climate models are
dependent) values lead to an almost equal weighting. Thus, an optimal choice
for $\sigma_D$ and $\sigma_S$ is crucial. A useful tool to estimate these
optimal parameters is the \emph{leave-one-model-out \ac{CV}} approach, which is
also known as \emph{pseudo-reality}, \emph{model-as-truth} or \emph{perfect
  model} setup \autocite{Elia2002, Karpechko2013}. For this, a single climate
model is removed from the multi-model ensemble and treated as observation
(\emph{pseudo-observation}). Then, a weighted \ac{MMM} with weights computed
from the updated model ensemble is calculated, which gives a prediction for the
\enquote{true} climate model. This allows a simple quantitative assessment of
the weighting scheme by calculating the \ac{RMSE} between the prediction and
the known ground truth of the pseudo-observation, which is also known as
\ac{RMSEP}. The whole process is repeated for every climate model of the
ensemble to get a statistical distribution of \acp{RMSEP}. Finally, different
\ac{RMSEP} distributions calculated from different parameters $\sigma_D$ and
$\sigma_S$ can be assessed using specific criteria to find optimal values for
$\sigma_D$ and $\sigma_S$ \autocite{Knutti2017a}. Furthermore, the
leave-one-model-out \ac{CV} approach can be used to evaluate different climate
model weightings schemes (including the unweighted \ac{MMM}) and compare them
against each other.

@@

An alternative climate model weighting scheme is the \emph{\ac{MDER}} approach
\autocite{Karpechko2013}. Similar to all methods presented in
\cref{sec:02:reducing_uncertainties}, it can be used to reduce uncertainties in
climate model projections with observations. The basis of \ac{MDER} is a set of
$K$ predictor diagnostics $\left\{ x^{(1)}, x^{(2)}, \ldots, x^{(K)} \right\}$
which are relevant for the projection of the target variable $y$. The reasoning
for this choice of the diagnostics is similar to the one presented in the
previous section: Weighting schemes should address the question \enquote{which
  climate model is adequate for predicting the target variable?} and not
\enquote{which climate model is the best?}.

>>>>

This \namecref{ch:02:scientific_background} introduces the scientific
background of this thesis. First, basic concepts of climate model simulations
and associated uncertainties are introduced (\cref{sec:02:esms}). Next,
important metrics describing climate sensitivity
(\cref{sec:02:climate_sensitivity}) and fundamental biogeochemical processes of
the global carbon cycle (\cref{sec:02:esms}) are presented. Finally,
state-of-the art techniques that can be used to reduce uncertainties in
projections of the future climate with observations are shown
(\cref{sec:02:reducing_uncertainties}). These methods form the basis for new
techniques developed in this thesis.

@@

In this thesis, climate model data from the two most recent \ac{CMIP}
generations is used, \acs{CMIP}5 and \acs{CMIP}6. More detailed information
about the specific variables and experiments analyzed is given in the
corresponding \namecrefs{ch:04:papers_ecs_tcr_assessment}.

@@

\emph{Natural variability} is connected to the chaotic nature of the Earth
system that arises from complex interactions between the ocean, atmosphere,
land, biosphere and cryosphere \autocite{Cubasch2013}. It constitutes a
fundamental limit of how precisely we can project the future climate since it
is inherent in the Earth system and cannot be eliminated by more knowledge and
more advanced climate models. Natural variability is more relevant on regional
and local scales than on continental or global scales. Further contributions to
natural variability on longer time scales come from phenomena like the
\ac{ENSO} or the \ac{NAO} and from externally (and thus explainable) events
like volcanic eruptions and variations in the solar activity. Natural
variability can be seen as the \enquote{noise} in the climate record as opposed
to the anthropogenic \enquote{signal} \autocite{Cubasch2013}. As illustrated by
\cref{fig:02:sources_of_uncertainty}, the uncertainty associated with natural
variability is constant over time.

@@

As sciences evolves, representations of already included processes can be
improved in climate models. Moreover, new geophysical and biogeochemical
processes can be added to them. On the one hand, this can increase the climate
response uncertainty when a new process is discovered to be relevant
\commentcite{Cubasch2013}{see
  \cref{fig:02:sources_of_uncertainty}{\color{BrownRed} b}}. However, such an
increase corresponds to a previously unmeasured uncertainty. An example for
this has recently happened in \acs{CMIP}6: most likely due to changes in the
cloud representation of the models the spread in the projected \ac{GSAT} caused
by a doubling of the atmospheric \ac{CO2} concentration has substantially
increased in \acs{CMIP}6 compared to older \ac{CMIP} generations
\autocite{Zelinka2020}. On the other hand, the climate response uncertainty can
decrease with additional model improvements and better understanding of the
Earth system (see \cref{fig:02:sources_of_uncertainty}{\color{BrownRed} c}).
Moreover, it can also be reduced by observational constraints, which is the
main topic of this thesis.

@@

Since one study presented in this thesis aims to reduce uncertainties in carbon
cycle--related processes \commentcite{Schlund2020}{see \cref{ch:06:paper_gpp}},
this \namecref{sec:02:carbon_cycle} introduces the scientific background of the
global carbon cycle.

@@

Thus, more sophisticated techniques are necessary to evaluate multi-model
climate projections. This \namecref{sec:02:reducing_uncertainties} introduces
three state-of-the-art methods to assess multi-model projections and reduce
associated uncertainties with observations. These techniques form the baseline
of the work presented in the following \namecrefs{ch:05:paper_ecs}.

@@

As indicated at the beginning of this \namecref{sec:02:reducing_uncertainties},
one main issue of multi-model ensembles is that not all participating climate
models are equally plausible. Usually, this is quantified with some kind of
measure of the models' \emph{performance}, \ie{} their agreement with
observations of the real climate system. However, this model performance can
only be evaluated against observations of the past and present-day climate,
which does not necessarily provide insights into the quality of model
projections of the future climate.

@@

A further technique to reduce uncertainties in climate model projections with
observations are model weighting schemes. Their basic idea is to abandon model
democracy by replacing the arithmetic mean used to calculate the \acp{MMM} by a
weighted mean of the form
\begin{equation}
  y = \sum_{m=1}^{M} w_m y_m
  \label{eq:02:weighted_mean}
\end{equation}
with normalized weights $w_m$. Similar to the notation introduced in the
previous \namecref{subsec:02:emergent_constraints}, $y$ is a target variable
(\eg{} a projection of the future climate) and $m$ indexes the $M$ different
climate models. To address two major issues of model democracy (different
climate models are not equally plausible and not independent; see beginning of
\cref{sec:02:reducing_uncertainties}), \textcite{Knutti2017a} propose a
weighting scheme based on climate model performance and interdependence with
the following weights:
\begin{equation}
  w_m \propto \frac{\exp \left( -\frac{D_m^2}{\sigma_D^2} \right)}{1 + \sum_{n
    \neq m}^{M} \exp \left( -\frac{S_{mn}^2}{\sigma_S^2} \right)}.
  \label{eq:02:knutti_weights}
\end{equation}
The metric $D_m$ describes the distance between climate model $m$ and
observations (= model performance) and the metric $S_{mn}$ describes the
distance between climate model $m$ and $n$ (= model interdependence).
$\sigma_D$ and $\sigma_S$ are constants that determine the individual strength
of the performance and interdependence weighting, respectively.

@@

The constants $\sigma_D$ and $\sigma_S$ determine how strongly the climate
models' performance and interdependence are weighted \autocite{Knutti2017a}.
Small values of the performance parameter $\sigma_D$ lead to an aggressive
weighting with only a few climate models receiving a majority of the weight,
while large values of $\sigma_D$ result in an equal weighting. For the
interdependence parameter $\sigma_S$, this is slightly different: Here, small
(all climate models are independent) and large (all climate models are
dependent) values lead to an almost equal weighting. Thus, an optimal choice
for $\sigma_D$ and $\sigma_S$ is crucial. A useful tool to estimate these
optimal parameters is the \emph{leave-one-model-out \ac{CV}} approach, which is
also known as \emph{pseudo-reality}, \emph{model-as-truth} or \emph{perfect
  model} setup \autocite{Elia2002, Karpechko2013}. For this, a single climate
model is removed from the multi-model ensemble and treated as observation
(\emph{pseudo-observation}). Then, a weighted \ac{MMM} with weights computed
from the updated model ensemble is calculated, which gives a prediction for the
\enquote{true} climate model. This allows a simple quantitative assessment of
the weighting scheme by calculating the \ac{RMSE} between the prediction and
the known ground truth of the pseudo-observation, which is also known as
\emph{\ac{RMSEP}}. The whole process is repeated for every climate model of the
ensemble to get a statistical distribution of \acp{RMSEP}. Finally, different
\ac{RMSEP} distributions calculated from different parameters $\sigma_D$ and
$\sigma_S$ can be assessed using specific criteria to find optimal values for
$\sigma_D$ and $\sigma_S$ \autocite{Knutti2017a}. Furthermore, the
leave-one-model-out \ac{CV} approach can be used to evaluate different climate
model weightings schemes (including the unweighted \ac{MMM}) and compare them
against each other.

@@

An alternative climate model weighting scheme is the \emph{\ac{MDER}} approach
\autocite{Karpechko2013}. Similar to all methods presented in
\cref{sec:02:reducing_uncertainties}, it can be used to reduce uncertainties in
climate model projections with observations. The basis of \ac{MDER} is a set of
$K$ predictor diagnostics $\left\{ x^{(1)}, x^{(2)}, \ldots, x^{(K)} \right\}$
which are relevant for the projection of the target variable $y$. The reasoning
for this choice of the diagnostics is similar to the one presented in the
previous \namecref{subsec:02:model_weighting}: Weighting schemes should address
the question \enquote{which climate model is adequate for predicting the target
  variable?} and not \enquote{which climate model is the best?}.

### 2021-02-19 ch03_esmvaltool/esmvaltool.tex
Finished section 6.1

In order to answer the key science questions of this thesis posed in
\cref{sec:01:research_questions}, a reliable and efficient tool to read,
process and evaluate climate model output and observational data is necessary.
A valuable software that fits these criteria is the \ac{ESMValTool}. The
\ac{ESMValTool} is an open-source community diagnostics and performance metrics
tool for the routine evaluation of \ac{ESM} output, which notably facilitates
the analysis of \ac{CMIP} models (\url{https://www.esmvaltool.org}). For this
reason, all analyses presented in
\cref{ch:04:papers_ecs_tcr_assessment,ch:05:paper_ecs,ch:06:paper_gpp} of this
thesis have been implemented into the \ac{ESMValTool}. Apart from that, further
substantial changes and additions to the code base of the \ac{ESMValTool} have
been contributed that improve the routine evaluation of climate models, which
is beneficial for the entire scientific community. This lead to co-authorship
in the scientific documentation of the \ac{ESMValTool}, which is published in
four peer-reviewed studies \autocite{Eyring2020, Lauer2020, Righi2020,
  Weigel2020}. After a brief overview of the \ac{ESMValTool}'s structure
(\cref{sec:03:esmvaltool}), this chapter presents all these contributions that
are not documented in other chapters of this thesis
(\cref{sec:03:contributions_to_esmvalcore,sec:03:contributions_to_esmvaltool}).

@@

In addition to the ported recipes, several new recipes and diagnostic scripts
have been contributed to the public \ac{ESMValTool} repository (see
\cref{tab:03:changes_to_esmvaltool} for a summary). Some of these include the
analyses performed in other chapters of this thesis, namely
\emph{recipe\_bock20jgr.yml} (\cref{ch:04:papers_ecs_tcr_assessment}),
\emph{recipe\_meehl20sciadv.yml} (\cref{ch:04:papers_ecs_tcr_assessment}),
\emph{recipe\_schlund20esd.yml} (\cref{ch:05:paper_ecs}) and
\emph{recipe\_schlund20jgr\_*.yml} (\cref{ch:06:paper_gpp}).
\emph{recipe\_ecs.yml} and \emph{recipe\_tcr.yml} contain diagnostic scripts
that are able to calculate the climate metrics \ac{ECS} and \ac{TCR} for
arbitrary model output (see \cref{sec:02:climate_sensitivity}). Corresponding
plots are shown in \cref{fig:02:gregory_regression,fig:02:tcr}.
\emph{recipe\_cox18nature.yml} reproduces the analysis of \textcite{Cox2018},
who introduce an emergent constraint in \ac{ECS} based on a global temperature
variability metric $\Psi$. \Cref{fig:03:cox18:a} shows $\Psi$ over the past 85
years for \acs{CMIP}5 models and observations form HadCRUT4
\autocite{Morice2012}. Since high-sensitivity climate models exhibit higher
values of $\Psi$ than low sensitivity models, an emergent relationship between
\ac{ECS} and $\Psi$ can be established (\cref{fig:03:cox18:b}). With
observations of $\Psi$, \ac{ECS} can eventually be constrained to $\left( 2.8
\pm 0.6 \right) \unit{K}$ ($66 \unit{\%}$ confidence range). More details on
this including the calculation of $\Psi$ are given in \cref{subsec:05:cox}.

>>>>

In order to answer the key science questions of this thesis posed in
\cref{sec:01:key_science_questions}, a reliable and efficient tool to read,
process and evaluate climate model output and observational data is necessary.
A valuable software that fits these criteria is the \ac{ESMValTool}. The
\ac{ESMValTool} is an open-source community diagnostics and performance metrics
tool for the routine evaluation of \ac{ESM} output, which notably facilitates
the analysis of \ac{CMIP} models (\url{https://www.esmvaltool.org}). For this
reason, all analyses presented in
\cref{ch:04:papers_ecs_tcr_assessment,ch:05:paper_ecs,ch:06:paper_gpp} of this
thesis have been implemented into the \ac{ESMValTool}. Apart from that, further
substantial changes and additions to the code base of the \ac{ESMValTool} have
been contributed that improve the routine evaluation of climate models, which
is beneficial for the entire scientific community. This lead to co-authorship
in the scientific documentation of the \ac{ESMValTool}, which is published in
four peer-reviewed studies \autocite{Eyring2020, Lauer2020, Righi2020,
  Weigel2020}. After a brief overview of the \ac{ESMValTool}'s structure
(\cref{sec:03:esmvaltool}), this \namecref{ch:03:esmvaltool} presents all these
contributions that are not documented in other
\namecrefs{ch:04:papers_ecs_tcr_assessment} of this thesis
(\cref{sec:03:contributions_to_esmvalcore,sec:03:contributions_to_esmvaltool}).

@@

In addition to the ported recipes, several new recipes and diagnostic scripts
have been contributed to the public \ac{ESMValTool} repository (see
\cref{tab:03:changes_to_esmvaltool} for a summary). Some of these include the
analyses performed in other \namecrefs{ch:04:papers_ecs_tcr_assessment} of this
thesis, namely \emph{recipe\_bock20jgr.yml}
(\cref{ch:04:papers_ecs_tcr_assessment}), \emph{recipe\_meehl20sciadv.yml}
(\cref{ch:04:papers_ecs_tcr_assessment}), \emph{recipe\_schlund20esd.yml}
(\cref{ch:05:paper_ecs}) and \emph{recipe\_schlund20jgr\_*.yml}
(\cref{ch:06:paper_gpp}). \emph{recipe\_ecs.yml} and \emph{recipe\_tcr.yml}
contain diagnostic scripts that are able to calculate the climate metrics
\ac{ECS} and \ac{TCR} for arbitrary model output (see
\cref{sec:02:climate_sensitivity}). Corresponding plots are shown in
\cref{fig:02:gregory_regression,fig:02:tcr}. \emph{recipe\_cox18nature.yml}
reproduces the analysis of \textcite{Cox2018}, who introduce an emergent
constraint in \ac{ECS} based on a global temperature variability metric $\Psi$.
\Cref{fig:03:cox18:a} shows $\Psi$ over the past 85 years for \acs{CMIP}5
models and observations form HadCRUT4 \autocite{Morice2012}. Since
high-sensitivity climate models exhibit higher values of $\Psi$ than low
sensitivity models, an emergent relationship between \ac{ECS} and $\Psi$ can be
established (\cref{fig:03:cox18:b}). With observations of $\Psi$, \ac{ECS} can
eventually be constrained to $\left( 2.8 \pm 0.6 \right) \unit{K}$ ($66
\unit{\%}$ confidence range). More details on this including the calculation of
$\Psi$ are given in \cref{subsec:05:cox}.
